---
title: "Customer Retention Improvement"
output: pdf_document
date: "2023-05-15"
---

## Read Data, Descriptive Stats, Variables Transformation
```{r setup, include=FALSE}
setwd("/Users/tsaiiyu/Desktop/0. Marketing Models/")
relay <- read.csv("relay.csv", head = TRUE)
str(relay)

relay$created <- as.numeric(as.Date(relay$created, format="%m/%d/%Y"))
relay$firstorder <- as.numeric(as.Date(relay$firstorder, format="%m/%d/%Y"))
relay$lastorder <- as.numeric(as.Date(relay$lastorder, format="%m/%d/%Y"))
relay$paperless <- as.factor(relay$paperless)
relay$refill <- as.factor(relay$refill)
relay$doorstep <- as.factor(relay$doorstep)
relay$favday <- as.factor(relay$favday)
relay$duration <- relay$lastorder - relay$created + 1
relay <- subset(relay, relay$duration > 0)
relay$cens <- ifelse(relay$retained == 0, 0, 1)
relay$highesent <- ifelse(relay$esent > 32, 1, 0)
summary(relay)

relay_1 <- relay[,c(6,7,8)]
pairs(relay_1)
cor(relay_1)

hist(relay$retained)
hist(relay$esent, breaks = 100)
hist(relay$eopenrate)
hist(relay$eclickrate)
hist(relay$avgorder)
hist(relay$ordfreq, breaks = 100)
table(relay$favday)
hist(relay$created)
hist(relay$firstorder)
hist(relay$lastorder)
```


## KM Plots
```{r}
km0.fit <- survfit(Surv(duration, cens == 0, type = "right") ~ 1, data = relay)
summary(km0.fit)
install.packages("survminer")
library(survminer)
ggsurvplot(km0.fit, conf.int = TRUE)

## esent
km1.fit <- survfit(Surv(duration, cens == 0, type = "right") ~ highesent, data = relay)
summary(km1.fit)
ggsurvplot(km1.fit, conf.int = TRUE, linetype = "strata")

## paperless
km2.fit <- survfit(Surv(duration, cens == 0, type = "right") ~ paperless, data = relay)
summary(km2.fit)
ggsurvplot(km2.fit, conf.int = TRUE, linetype = "strata")

## refill
km3.fit <- survfit(Surv(duration, cens == 0, type = "right") ~ refill, data = relay)
summary(km3.fit)
ggsurvplot(km3.fit, conf.int = TRUE, linetype = "strata")

## doorstep
km4.fit <- survfit(Surv(duration, cens == 0, type = "right") ~ doorstep, data = relay)
summary(km4.fit)
ggsurvplot(km4.fit, conf.int = TRUE, linetype = "strata")
```


## Binary Dependent Variable: retained (0/1)
### 1) Linear Probability Model
```{r}
fit_lpm <- lm(retained ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + doorstep + favday, family = binomial, relay)
summary(fit_lpm)

library(car)
vif(fit_lpm) ## no multicollinearity
```



### 2) Logit Regression Model
```{r}
fit_logit <- glm(retained ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + doorstep + favday, family = binomial(link = logit), relay)
summary(fit_logit)

## LRT to test model significane and variables significance
install.packages("lmtest")
library(lmtest)

lrtest(fit_logit)

logit_restr1 <- glm(retained ~ log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + doorstep + favday, family = binomial(link = logit), relay)
lrtest(logit_restr1, fit_logit) ## esent is significant.

logit_restr2 <- glm(retained ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + refill + doorstep + favday, family = binomial(link = logit), relay)
lrtest(logit_restr2, fit_logit) ## paperless is significant.

logit_restr3 <- glm(retained ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + doorstep + favday, family = binomial(link = logit), relay)
lrtest(logit_restr3, fit_logit) ## refill is significant.

logit_restr4 <- glm(retained ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + favday, family = binomial(link=logit), relay)
lrtest(logit_restr4, fit_logit) ## doorstep is not significant.
```


### 3) Probit Regression Model
```{r}
fit_probit <- glm(retained ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + doorstep + favday, family = binomial(link = probit), relay)
summary(fit_probit)

## LRT to test model significane and variables significance
lrtest(fit_probit)

probit_restr1 <- glm(retained ~ log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + doorstep + favday, family = binomial(link = probit), relay)
lrtest(probit_restr1, fit_probit) ## esent is significant.

probit_restr2 <- glm(retained ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + refill + doorstep + favday, family = binomial(link = probit), relay)
lrtest(probit_restr2, fit_probit) ## paperless is significant.

probit_restr3 <- glm(retained ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + doorstep + favday, family = binomial(link = probit), relay)
lrtest(probit_restr3, fit_probit) ## refill is significant.

probit_restr4 <- glm(retained ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + favday, family = binomial(link = probit), relay)
lrtest(probit_restr4, fit_probit) ## doorstep is not significant.
```


## Right-censored time to event variable: retained duration
### 1) Weibull Accelerated Failure Time (AFT) Model
```{r}
install.packages("survival")
library(survival)

wei.fit <- survreg(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + doorstep + favday, data = relay, dist = "weibull")
summary(wei.fit)


# LRT to test model significane and variables significance
wei_restr1 <- survreg(Surv(duration, cens == 0, type = "right") ~ log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + doorstep + favday, data = relay, dist = "weibull")
lrtest(wei_restr1, wei.fit) ## esent is significant.

wei_restr2 <- survreg(Surv(duration, cens == 0, typ = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + refill + doorstep + favday, data = relay, dist = "weibull")
lrtest(wei_restr2, wei.fit) ## paperless is significant.

wei_restr3 <- survreg(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + doorstep + favday, data = relay, dist = "weibull")
lrtest(wei_restr3, wei.fit) ## refill is significant.

wei_restr4 <- survreg(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + favday, data = relay, dist = "weibull")
lrtest(wei_restr4, wei.fit) # doorstep is not significant.
```


### 2) Weibull Proportional Hazard (PH) Model
```{r}
p = 1/wei.fit$scale
p
wei_ph.beta = (-1)*p*wei.fit$coeff
wei_ph.beta
```


### 3) Exponential Accelerated Failure Time (AFT) Model
```{r}
exp.fit <- survreg(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + doorstep + favday, data = relay, dist = "exponential")
summary(exp.fit)


# LRT to test model significance and variables significance
exp_restr1 <- survreg(Surv(duration, cens == 0, type = "right") ~ log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + doorstep + favday, data = relay, dist = "exponential")
lrtest(exp_restr1, exp.fit) ## esent is significant.

exp_restr2 <- survreg(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + refill + doorstep + favday, data = relay, dist = "exponential")
lrtest(exp_restr2, exp.fit) ## paperless is significant.

exp_restr3 <- survreg(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + doorstep + favday, data = relay, dist = "exponential")
lrtest(exp_restr3, exp.fit) ## refill is significant

exp_restr4 <- survreg(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + favday, data = relay, dist = "exponential")
lrtest(exp_restr4, exp.fit) ## doorstep is not significant.

```

### 4) Exponential Proportional Hazard (PH) Model
```{r}
exp_ph.beta = (-1)*exp.fit$coeff
exp_ph.beta
```

### 5) Lognormal Model
```{r}
# Lognormal AFT
logn.fit <- survreg(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + doorstep + favday, data = relay, dist = "lognormal")
summary(logn.fit)

# LRT
logn_restr1 <- survreg(Surv(duration, cens == 0, type = "right") ~ log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + doorstep + favday, data = relay, dist = "lognormal")
lrtest(logn_restr1, logn.fit) ## esent is significant.

logn_restr2 <- survreg(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + refill + doorstep + favday, data = relay, dist = "lognormal")
lrtest(logn_restr2, logn.fit) ## paperless is significant.

logn_restr3 <- survreg(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + doorstep + favday, data = relay, dist = "lognormal")
lrtest(logn_restr3, logn.fit) ## refill is significant.

logn_restr4 <- survreg(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + favday, data = relay, dist = "lognormal")
lrtest(logn_restr4, logn.fit) ## doorstep is not significant.

```


### 6) Loglogistic AFT model
```{r}
loglog.fit <- survreg(formula = Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate+1) + log(eclickrate+1) + log(avgorder+1) + log(ordfreq+1) + paperless + refill + doorstep + favday, data = relay, dist = "loglogistic")
summary(loglog.fit)

# LRT
loglog_restr1 <- survreg(Surv(duration, cens == 0, type = "right") ~ log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + doorstep + favday, data = relay, dist = "loglogistic")
lrtest(loglog_restr1, loglog.fit) ## esent is significant.

loglog_restr2 <- survreg(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + refill + doorstep + favday, data = relay, dist = "loglogistic")
lrtest(loglog_restr2, loglog.fit) ## paperless is significant.

loglog_restr3 <- survreg(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + doorstep + favday, data = relay, dist = "loglogistic")
lrtest(loglog_restr3, loglog.fit) ## refill is significant.

loglog_restr4 <- survreg(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + favday, data = relay, dist = "loglogistic") 
lrtest(loglog_restr4, loglog.fit) ## doorstep is not significant.
```


### 7) Cox PH Model
```{r}
# Cox PH
cox.fit <- coxph(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + doorstep + favday, data = relay)
summary(cox.fit)


# LRT
cox_restr1 <- coxph(Surv(duration, cens == 0, type = "right") ~ log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + doorstep + favday, data = relay)
lrtest(cox_restr1, cox.fit) ## esent is significant.

cox_restr2 <- coxph(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1)+ refill + doorstep + favday, data = relay)
lrtest(cox_restr2, cox.fit) ## paperless is significant.

cox_restr3 <- coxph(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + doorstep + favday, data = relay)
lrtest(cox_restr3, cox.fit) ## refill is significant.

cox_restr4 <- coxph(Surv(duration, cens == 0, type = "right") ~ esent + log(eopenrate + 1) + log(eclickrate + 1) + log(avgorder + 1) + log(ordfreq + 1) + paperless + refill + favday, data = relay)
lrtest(cox_restr4, cox.fit) ## doorstep is not significant.
```




